Sketch Recognition and Understanding

### 2009-07-28 trunk/draft/chapterSurvey.tex
change i mad for pso1

 The comparison between PSO and Genetic algorithm was performed in \cite{PSOGAComp} and proved that PSO generate faster, better optimal solutions than GA especially in problems with high dimensionality. In addition, Rohinsons et al. \cite{RohinsonPSGA} proved that PSO performed better than GA in difficult engineering problems \cite{EngineerProblemGA}.

% Eberhart \cite{PSOGAComp}

>>>>

 The comparison between PSO and Genetic algorithm was performed in \cite{PSOGAComp,} and proved that PSO generate faster, better optimal solutions than GA especially in problems with high dimensionality. In addition, Rohinsons et al. \cite{RohinsonPSGA} proved that PSO performed better than GA in difficult engineering problems \cite{EngineerProblemGA}.

% Eberhart \cite{PSOGAComp}
%%PSO has been shown to have the same ability to find a global optimum as genetic
%algorithms, but is able to find optimums faster than genetic algorithms (Panda and Padhy
%2007; Mouser and Dunn 2005; Hassan et al. 2005)
